### 2012-09-20 doc/prelim/document/chapters/linear_problem/linear_problem.tex
Working on monte carlo domain decomposition section

\subsubsection{Multiple-Set Overlapping-Domain Decomposition}
\label{subsubsec:msod}
As observed in the discussion on parallel Krylov methods, large-scale
problems will surely have their data partitioned such that each
parllel process owns a subset of the equations in the linear
system. Given this convention, the adjoint Monte Carlo algorithm must
perform random walks over a domain that is decomposed and must remain
decomposed due to memory limitations. This naturally leads us to seek
parallel algorithms that handle domain decomposition. In 2010, Wagner
and colleagues developed the \textit{multiple-set overlapping-domain}
(MSOD) decomposition for parallel Monte Carlo applications for
full-core reactor analysis \citep{wagner_hybrid_2010}.

>>>>

\subsubsection{Domain Decomposition for Monte Carlo}
\label{subsubsec:msod}
As observed in the discussion on parallel Krylov methods, large-scale
problems will surely have their data partitioned such that each
parllel process owns a subset of the equations in the linear
system. Given this convention, the adjoint Monte Carlo algorithm must
perform random walks over a domain that is decomposed and must remain
decomposed due to memory limitations. This naturally leads us to seek
parallel algorithms that handle domain decomposition. In the context
of radiation transport, Brunner and colleagues provided one of the
first surveys of algorithms for achieving this
\citep{brunner_comparison_2006}. In their work they identity two data
sets that are required to be communicated: the sharing of particles
that are transported from one domain to another and therefore from one
processor to another and a global communication that signals if
particle transport has been completed on all processors. The
algorithms presented include a fully-locking synchronous scheme, a
fully-asynchronous pattern, a traditional master/slave scheme, and a
modified master/slave scheme the implements a binary tree pattern for
the global reduction type operations needed to communicate between the
master and slave processes.

In 2010, Wagner and colleagues developed the \textit{multiple-set
  overlapping-domain} (MSOD) decomposition for parallel Monte Carlo
applications for full-core reactor analysis
\citep{wagner_hybrid_2010}.
